---
title: "Estimating Parameter"
author: "Leo Zhao"
output: pdf_document
---

```{r,echo = FALSE}
# load data
load(file = "data/transfordata.rdata")
```


# Exposure Analysis 

```{r,echo = FALSE,message = FALSE}
library(dplyr)
library(ggplot2)
```


```{r }
# personal : getting total exposure for personal type
P = data %>% filter(Type == "Personal") %>% group_by(Year,Quarter) %>% summarize(total = sum(CarYearsOfExposure)/5)%>% mutate(time = Year + (as.numeric(Quarter)-1)*0.25)

# Commercial : getting total exposure for commercial type
C = data %>% filter(Type == "Commercial") %>% group_by(Year,Quarter) %>% summarize(total = sum(CarYearsOfExposure)/5)%>% mutate(time = Year + (as.numeric(Quarter)-1)*0.25)

# adding the quarterly total to the original data
timeTotalExposure = data %>% group_by(Year,Quarter,Type) %>% summarize(total = sum(CarYearsOfExposure)/5)%>% mutate(time = Year + (as.numeric(Quarter)-1)*0.25)
data = inner_join(data,timeTotalExposure)
```

```{r,fig.cap="figure 4-1",fig.height=6, fig.width=8}
par(mfrow = c(2,1))
plot(P$time,P$total,main = "Total Exposure in traditional car industry:Type Personal",type = "o",ylab = "Exposure",xlab = "Year")
plot(C$time,C$total,main = "Total Exposure in traditional car industry:Type Commercial",type = "o",ylab = "Exposure",xlab = "Year")
```

```{r}
library(forecast)
Personal = timeTotalExposure[timeTotalExposure$Type=="Personal",]
Personal = Personal$total
Personal = ts(Personal,start = 2009,freq = 4)
ts.plot(Personal,ylab = "total exposure")
```

- calculate $y_t-y_{t-1}$,setting as D
```{r}
D = Personal[2:40]-Personal[1:39]
ts.plot(D)
acf(D,lag.max = 30)
```

exist some seasonal pattern, stationary 

```{r}

M = factor(rep(1:4, length.out=length(D)), levels=1:4)
mod3 = lm(D~time(D)+M+0)
summary(mod3)
plot(D, type="o")
lines(as.numeric(time(D)),mod3$fitted.values, col="pink2", lwd=2)
plot(mod3)
sigma = sqrt(sum(mod3$residuals^2)/34)
sigma 
```

# Estimate the exposure of personal type in the next 12 years

```{r fig.height=4, fig.width=12}
result = data.frame()
for(i in 40:87){
    seasonTerm = i%%4
    if(seasonTerm == 0){
        ST = mod3$coefficients[5]
    }
    else{
        ST = mod3$coefficients[seasonTerm+1]
    }
    ED = mod3$coefficients[1]*i+ST
    level95 = ED+c(-1.96,1.96)*sigma
    if(i == 40){
       exp = Personal[40]+level95
    }
    else{
       exp[1] = result[i-40,1]+level95[1]
       exp[2] = result[i-40,2]+level95[2]
    }
    result = rbind(result,exp)
}
upperboundLimit = ts(result[,2],start = 2019,freq = 4)
LowerboundLimit = ts(result[,1],start = 2019,freq = 4)

```


```{r}
Commercial = timeTotalExposure[timeTotalExposure$Type=="Commercial",]
Commercial = Commercial$total
Commercial = ts(Commercial,start = 2009,freq = 4)
ts.plot(Commercial,ylab = "total exposure")
```

- calculate $y_t-y_{t-4}$,setting as D
```{r}
D1 = Commercial[5:40]-Commercial[1:36]
ts.plot(D1)
acf(D1)
pacf(D1)
```

exist some seasonal pattern, stationary 

```{r}
mod4 = Arima(D1,c(4,0,1))
mod4
summary(mod4)
plot(D1, type="o")
lines(as.numeric(time(D1)),D1-mod4$residuals, col="pink2", lwd=2)

qqplot(x = qnorm(ppoints(mod4$residuals), mean = mean(mod4$residuals), sd = sd(mod4$residuals)),y = mod4$residuals,xlab = "Theoretical Quantiles, Normal Distribution",ylab = "Sample Quantiles")
abline(a = 0,b=1)

acf(mod4$residuals)

residComer = mod4$residuals
```


# Estimate the exposure of Commercial type in the next 12 years

```{r}
commercialResult = forecast(mod4,h=48,level = 0.95)
commercialResult = data.frame(commercialResult)
result2 = data.frame()
for(i in 41:88){
    if(i-4 <=40){
       exp = Commercial[i-4]+commercialResult[i-40,2:3]
    }
    else{
       exp[1] = result2[i-44,1]+commercialResult[i-40,2]
       exp[2] = result2[i-44,2]+commercialResult[i-40,3]
    }
    result2= rbind(result2,exp)
}

upperboundLimit2 = ts(result2[,2],start = 2019,freq = 4)
LowerboundLimit2 = ts(result2[,1],start = 2019,freq = 4)

```

# Chart for prediction interval
```{r fig.height=6, fig.width=8}
par(mfrow = c(2,1))
ts.plot(upperboundLimit,ylim = c(200000,700000),ylab = "exposure",type = "o",main = "95% prediction interval for the exposure until 2030:PersonalType",xlab="Year")
points(LowerboundLimit,type = "o")
ts.plot(upperboundLimit2,ylim = c(80000,200000),ylab = "exposure",type = "o",main = "95% prediction interval for the exposure until 2030:CommercialType",xlab = "Year")
points(LowerboundLimit2,type = "o")
```





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Market share of autonomous car

account for 20% - 25% 
- assuming the autonomous car grow in exponential rate

```{r}
MarketShare = seq(2,20,18/43)
MarketShareUp = seq(5,25,20/43)
estimateAVS = (MarketShare+MarketShareUp)/2
estimateAVS
plot(seq(2020,2030.75,0.25),estimateAVS,xlab = "year",main = "Percentage of new vehicles per year sold that are autonomous",ylim = c(0,25),ylab = "Percentage",type = "l")
```

```{r}
LowerboundLimitAVP = ts(LowerboundLimit[5:48]/(1-estimateAVS/100)*estimateAVS/100,start = c(2020,1),freq = 4)
upperboundLimitAVP = ts(upperboundLimit[5:48]/(1-estimateAVS/100)*estimateAVS/100,start = c(2020,1),freq = 4)
LowerboundLimitAVC = ts(LowerboundLimit2[5:48]/(1-estimateAVS/100)*estimateAVS/100,start = c(2020,1),freq = 4)
upperboundLimitAVC = ts(upperboundLimit2[5:48]/(1-estimateAVS/100)*estimateAVS/100,start = c(2020,1),freq = 4)
```

# Chart for prediction interval of autonomous car
```{r fig.height=6, fig.width=8}
par(mfrow = c(2,1))
ts.plot(upperboundLimitAVP,ylim = c(0,200000),ylab = "exposure",type = "o",main = "95% prediction interval for the exposure of AVs until 2030:PersonalType",xlab="Year")
points(LowerboundLimitAVP,type = "o")
ts.plot(upperboundLimitAVC,ylim = c(0,80000),ylab = "exposure",type = "o",main = "95% prediction interval for the exposure of AVsuntil 2030:CommercialType",xlab = "Year")
points(LowerboundLimitAVC,type = "o")
```

# frequency and severity level
```{r}
NC = aggregate(data$NumberOfClaim,by = list(data$Type,data$time),sum)
NP = aggregate(data$CarYearsOfExposure,by = list(data$Type,data$time),sum)
AC = aggregate(data$AmountOfClaim,by = list(data$Type,data$time),sum)

NP$x = NP$x/5

frequency = NC$x/NP$x
severity =  AC$x/NC$x
plot(NP$Group.2[which(NP$Group.1=="Commercial")],frequency[which(NP$Group.1=="Commercial")],xlab = "Year",ylim = c(0.5,0.8),ylab = "frequency",main = "frequency level for each type through time")
points(NP$Group.2[which(NP$Group.1=="Personal")],frequency[which(NP$Group.1=="Personal")],col = "red")
legend("topright", legend=c(expression(paste("Commercial")),
        expression("Personal")),
        col=c("black", "red"), lwd=c(1,2), cex=1)

plot(NP$Group.2[which(NP$Group.1=="Commercial")],severity[which(NP$Group.1=="Commercial")],xlab = "Year",ylab = "severity",main = "severity level for each type through time")
points(NP$Group.2[which(NP$Group.1=="Personal")],severity[which(NP$Group.1=="Personal")],col = "red")
legend("topright", legend=c(expression(paste("Commercial")),
        expression("Personal")),
        col=c("black", "red"), lwd=c(1,2), cex=1)
```

# Incured loss by year

```{r}
loss = c(133968451.8,213652512.7,302622117.2,
401921268.6,
512714679.8,
636302655.3,
774137368.6,
927841721.9,
1099230368,
1290333490,
1503423643)

purePremiumL = ts(loss/upperboundLimitAVP[seq(4,44,4)],start = 2020)
purePremiumH = ts(loss/LowerboundLimitAVP[seq(4,44,4)],start = 2020)
ts.plot(purePremiumL,ylim = c(0,25000),ylab = "premium",type = "o",main = "pure premium for autonomous car",xlab = "Year")
points(purePremiumH,type = "o")

```


